---
format:
  revealjs: 
    theme: [default, styles.scss]
    width: 1280
    height: 720
    include-after-body: 
      - "all-the-js-code.html"
echo: false
code-line-numbers: false
---

## Feature Engineering {.theme-title .center}

### SoCal RUG 2024 Hackathon

Emil Hvitfeldt

## What is Feature Engineering?

::: fragment
::: r-fit-text
The act of modifying data  
to allow for easy  
[extraction of signal]{.pink-shadow} and  
[elimination of noise]{.blue-shadow} 
:::
:::

##

::: {.speech .pink}
![](assets/cat-theme/profile-01.svg) why do we use feature engineering?
:::

::: fragment
::: {.speech .purple .right}
most models can't handle non-numeric data ![](assets/cat-theme/profile-02.svg) 
:::
:::

::: fragment
::: {.speech .blue}
![](assets/cat-theme/profile-03.svg) and we often have non-numeric data
:::
:::

##

::: {.speech .pink}
![](assets/cat-theme/profile-01.svg) Are there other reason?
:::

::: fragment
::: {.speech .brown .right}
to deal with missing values ![](assets/cat-theme/profile-04.svg) 
:::
:::

::: fragment
::: {.speech .blue .right}
and correlated features ![](assets/cat-theme/profile-05.svg)
:::
:::

::: fragment
::: {.speech .purple .right}
or deal with scaling issues ![](assets/cat-theme/profile-06.svg)
:::
:::

# {.theme-section2}

::: {.r-fit-text style="transform: translateY(-15rem);"}
preprocessing vs feature engineering 
:::

## 

![](assets/cat-theme/head-01.svg){.absolute bottom=0 right=0 width="150" height="150"}

::: {.columns}
::: {.column}

### Preprocessing

[what needs to happen]{.blue-text}

<br>

::: fragment
transformation

Normalization

Formatting

Imputing

Encoding
:::


:::
::: {.column}

### Feature engineering

[what helps capture signal]{.purple-text}

<br>

::: fragment
transformation

Normalization

Formatting

Imputing

Encoding
:::

:::
:::

## Long Beach Animal Shelter Data

![](assets/cat-theme/head-02.svg){.absolute top=-50 right=300 width="150" height="150"}
![](assets/cat-theme/head-03.svg){.absolute top=-50 right=150 width="150" height="150"}
![](assets/cat-theme/head-04.svg){.absolute top=-50 right=0 width="150" height="150"}

```{r}
library(tidyverse)
library(janitor)
library(gt)

adoptions <- read_csv("data/animal-shelter-intakes-and-outcomes.csv") |>
  clean_names() |>
  filter(animal_type == "CAT")

adoptions |>
  head(n = 10) |>
  gt()
```

::: footer
<https://data.longbeach.gov/explore/dataset/animal-shelter-intakes-and-outcomes>
:::

## Date Time

![](assets/cat-theme/head-06.svg){.absolute top=0 right=0 width="150" height="150"}

How can we deal with this variable?

::::: {.columns}

::::: {.column width="20%"}
```{r}
adoptions |>
  select(intake_date) |>
  head(n = 10) |>
  gt()
```
:::::

::::: {.column width="80%"}
::: r-stack

::: {.fragment .fade-in-then-out}
```{r}
adoptions |>
  select(intake_date) |>
  transmute(intake_date_integer = as.integer(intake_date)) |>
  head(n = 10) |>
  gt()
```
:::

::: {.fragment .fade-in-then-out}
:::

::: {.fragment .fade-in-then-out}
```{r}
adoptions |>
  select(intake_date) |>
  transmute(
    intake_date_year = clock::get_year(intake_date),
    intake_date_month = clock::get_month(intake_date),
    intake_date_day = clock::get_day(intake_date)
  ) |>
  head(n = 10) |>
  gt()
```
:::

::: {.fragment .fade-in-then-out}
:::

::: {.fragment .fade-in-then-out}
```{r}
library(extrasteps)
library(almanac)

rules <- list(christmas = hol_christmas(), halloween = hol_halloween())

recipe(~ intake_date, data = adoptions) |>
  step_date_before(intake_date, rules = rules) |>
  prep() |>
  bake(NULL) |>
  head(n = 10) |>
  gt()
```
:::

::: {.fragment .fade-in-then-out}
```{r}
library(extrasteps)
library(almanac)

rules <- list(christmas = hol_christmas(), halloween = hol_halloween())

recipe(~ intake_date, data = adoptions) |>
  step_date_before(intake_date, rules = rules, transform = "log") |>
  prep() |>
  bake(NULL) |>
  head(n = 10) |>
  gt()
```
:::

:::
:::::
:::::

## Multiple Categorical variables

![](assets/cat-theme/head-07.svg){.absolute top=-50 right=300 width="150" height="150"}
![](assets/cat-theme/head-08.svg){.absolute top=-50 right=150 width="150" height="150"}

How can we deal with these variables?

```{r}
adoptions |>
  select(primary_color, secondary_color) |>
  head(n = 10) |>
  gt()
```

## Multiple Categorical variables

![](assets/cat-theme/head-07.svg){.absolute top=-50 right=300 width="150" height="150"}
![](assets/cat-theme/head-08.svg){.absolute top=-50 right=150 width="150" height="150"}

How can we deal with these variables? Create dummies

```{r}
adoptions |>
  select(primary_color, secondary_color) |>
  recipe() |>
  step_unknown(secondary_color) |>
  step_dummy(primary_color, secondary_color) |>
  prep() |>
  bake(NULL) |>
  head(n = 10) |>
  gt()
```

## Multiple Categorical variables

![](assets/cat-theme/head-07.svg){.absolute top=-50 right=300 width="150" height="150"}
![](assets/cat-theme/head-08.svg){.absolute top=-50 right=150 width="150" height="150"}

How can we deal with these variables? othering of low counts

```{r}
adoptions |>
  select(primary_color, secondary_color) |>
  recipe() |>
  step_unknown(secondary_color) |>
  step_other(primary_color, secondary_color, threshold = 0.01, other = "OTHER") |>
  step_dummy(primary_color, secondary_color) |>
  prep() |>
  bake(NULL) |>
  head(n = 10) |>
  gt()
```

## Multiple Categorical variables

![](assets/cat-theme/head-07.svg){.absolute top=-50 right=300 width="150" height="150"}
![](assets/cat-theme/head-08.svg){.absolute top=-50 right=150 width="150" height="150"}

How can we deal with these variables? combined dummies

```{r}
adoptions |>
  select(primary_color, secondary_color) |>
  recipe() |>
  step_unknown(secondary_color) |>
  step_dummy_multi_choice(primary_color, secondary_color, threshold = 0.019, other = "OTHER", prefix = "color") |>
  prep() |>
  bake(NULL) |>
  relocate(color_ORANGE, color_WHITE) |>
  head(n = 10) |>
  gt()
```

## What will we go over?

![](assets/cat-theme/head-10.svg){.absolute top=-50 right=150 width="150" height="150"}
![](assets/cat-theme/head-11.svg){.absolute top=300 right=700 width="150" height="150"}
![](assets/cat-theme/head-12.svg){.absolute bottom=0 right=0 width="150" height="150"}

::: {.columns}
::: {.column}

**Types of data**

- [numeric]{.fragment .highlight-purple fragment-index=1}
- [character]{.fragment .highlight-purple fragment-index=1}
  - factors
  - logical
- Datetime
- text
- image
- time series
- ... and more

:::
::: {.column}

**Data problems**

- [missing data]{.fragment .highlight-blue fragment-index=2}
- too many variables
- correlated variables
- [outliers]{.fragment .highlight-blue fragment-index=2}
- imbalanced
- ... and more
:::
:::

# numeric variables {.theme-section3}

##

::: {.speech .pink}
![](assets/cat-theme/profile-01.svg) Aren't we done? we have numeric variables
:::

::: fragment
::: {.speech .blue .right}
They might still need improvements ![](assets/cat-theme/profile-05.svg) 
:::
:::

::: fragment
::: {.speech .brown .right}
Distributional problems, scaling, outliers, non-linear effects ![](assets/cat-theme/profile-03.svg) 
:::
:::

## Distributional problems

![](assets/cat-theme/head-14.svg){.absolute top=400 left=300 width="150" height="150"}
![](assets/cat-theme/head-15.svg){.absolute top=400 left=50 width="150" height="150"}
![](assets/cat-theme/head-16.svg){.absolute top=200 left=300 width="150" height="150"}
![](assets/cat-theme/head-17.svg){.absolute top=200 left=50 width="150" height="150"}

::: {.spacer style="height:70%; text-align: right;"}

Think about how models are working

Very valid for count data

We **rarely** care whether a predictor is normal

:::

## A skewed distribution

```{r}
library(modeldata)

ames |>
  ggplot(aes(Lot_Area)) +
  geom_histogram(fill = "#ECC0CF", color = prismatic::clr_darken("#ECC0CF", 0.1), bins = 100) +
  theme_minimal() +
  labs(x = NULL, y = NULL)
```

## A logged skewed distribution

```{r}
library(modeldata)

ames |>
  ggplot(aes(log(Lot_Area))) +
  geom_histogram(fill = "#ECC0CF", color = prismatic::clr_darken("#ECC0CF", 0.1), bins = 100) +
  theme_minimal() +
  labs(x = NULL, y = NULL)
```

## A square rooted skewed distribution

```{r}
library(modeldata)

ames |>
  ggplot(aes(sqrt(Lot_Area))) +
  geom_histogram(fill = "#ECC0CF", color = prismatic::clr_darken("#ECC0CF", 0.1), bins = 100) +
  theme_minimal() +
  labs(x = NULL, y = NULL)
```

## Methods to alter distributions

![](assets/cat-theme/head-18.svg){.absolute bottom=150 left=300 width="150" height="150"}
![](assets/cat-theme/head-19.svg){.absolute bottom=-50 right=150 width="150" height="150"}

::: columns
::: {.column width="50%"}
- Logarithms
- Square Roots
- [Box-Cox]{.fragment .highlight-blue fragment-index=1}
- Yeo-Johnson
:::

::: {.column width="50%"}
::: {.fragment fragment-index=1}
using MLE to estimate a transformation parameter [$\lambda$]{.purple-color} in the following equation that would optimize the normality of $x^*$

$$
x^* = \left\{
    \begin{array}{ll}
      \dfrac{x^\lambda - 1}{\lambda \tilde{x}^{\lambda - 1}}, & \lambda \neq 0 \\
      \tilde{x} \log x & \lambda = 0
    \end{array}
  \right.
$$
:::
:::
:::

## Scaling issues

::: {.spacer style="height:70%;"}

Think about how models are working

- [tree based]{.text-pink} models doesn't care
- [distance based]{.text-brown} models do

has **few downsides** to doing

will make interpretations slightly harder
:::

## Motivated example

```{r}
set.seed(1234)
two_groups <- bind_rows(
  tibble(group = "A", x = rnorm(100, 0, 10), y = rnorm(100, 0, 1)),
  tibble(group = "B", x = rnorm(100, 100, 10), y = rnorm(100, 10, 1))
)

two_groups |>
  ggplot(aes(x, y, color = group)) +
  geom_point() +
  theme_minimal() +
  labs(x = NULL, y = NULL) +
  guides(color = "none") +
  scale_color_manual(values = c("#DFD0C0", "#D1BCDC")) +
  xlim(c(-35, 135)) +
  ylim(c(-5, 15))
```

## Motivated example

```{r}
two_groups |>
  ggplot(aes(x, y, color = group)) +
  geom_point() +
  theme_minimal() +
  labs(x = NULL, y = NULL) +
  guides(color = "none") +
  scale_color_manual(values = c("#DFD0C0", "#D1BCDC", "#B5C7EB")) +
  geom_point(data = tibble(group = "C", x = 45, y = 12), size = 4) +
  xlim(c(-35, 135)) +
  ylim(c(-5, 15))
```

## Motivated example

```{r}
grid <- expand_grid(y = seq(-5, 15, length.out = 200), x = seq(-35, 135, length.out = 200)) |>
  mutate(distA = sqrt((x-0)^2 + (y-0)^2)) |>
  mutate(distB = sqrt((x-100)^2 + (y-10)^2)) |>
  mutate(group = if_else(distA < distB, "A", "B"))

two_groups |>
  ggplot(aes(x, y, color = group)) +
  geom_point() +
  theme_minimal() +
  labs(x = NULL, y = NULL) +
  guides(color = "none", fill = "none") +
  scale_color_manual(values = c("#DFD0C0", "#D1BCDC", "#B5C7EB")) +
  scale_fill_manual(values = c("#DFD0C0", "#D1BCDC", "#B5C7EB")) +
  geom_raster(data = grid, aes(fill = group), alpha = 0.5) +
  geom_point(data = tibble(group = "C", x = 45, y = 12), size = 4) +
  xlim(c(-35, 135)) +
  ylim(c(-5, 15))
```

## Motivated example

```{r}
two_groups |>
  ggplot(aes(x, y, color = group)) +
  geom_point() +
  theme_minimal() +
  labs(x = NULL, y = NULL) +
  guides(color = "none") +
  scale_color_manual(values = c("#DFD0C0", "#D1BCDC", "#B5C7EB")) +
  geom_point(data = tibble(group = "C", x = 45, y = 12)) +
  coord_fixed()
```

## Scaling Methods

![](assets/cat-theme/turso-01.svg){.absolute top=150 right=100 width="300" height="300"}

All scaling methods are **trained** on our data

<br>

All are a variation on

$$
X_{scaled} = \dfrac{X - a}{b}
$$

<br>

either to change [magnitude]{.brown-text} of data, or its [range]{.purple-text}

## Scaling Methods

| Method        | Definition                                                               |
|----------------|--------------------------------------------------------|
| Max-Abs       | $X_{scaled} = \dfrac{X}{\text{max}(\text{abs}(X))}$                      |
| Normalization | $X_{scaled} = \dfrac{X - \text{mean}(X)}{\text{sd}(X)}$                  |
| Min-Max       | $X_{scaled} = \dfrac{X - \text{min}(X)}{\text{max}(X) - \text{min}(X)}$  |
| Robust        | $X_{scaled} = \dfrac{X - \text{median}(X)}{\text{Q3}(X) - \text{Q1}(X)}$ |

## Dealing with outliers

![](assets/cat-theme/head-20.svg){.absolute top=50 right=300 width="150" height="150"}
![](assets/cat-theme/head-21.svg){.absolute bottom=50 right=150 width="150" height="150"}

<br>

What are outliers?

<br>

::: fragment

::: r-fit-text
values that are [substantially different]{.blue-text}  
from the rest of the values
:::

:::

## Dealing with outliers

![](assets/cat-theme/head-22.svg){.absolute top=50 right=150 width="150" height="150"}
![](assets/cat-theme/head-23.svg){.absolute bottom=50 right=300 width="150" height="150"}

<br>

1. [Identify them]{.pink-text}
    a. expert knowledge
    b. (not recommended) thresholding
2. [Dealing with them]{.blue-text}
    a. removal
    b. imputation
    c. indication

## Non-linear effects

![](assets/cat-theme/head-24.svg){.absolute top=50% right=300 width="150" height="150"}


::: {.spacer style="height:70%;"}

Doing a linear effect, we have that when the predictor [increases in value]{.brown-text}, the outcome [increases in value]{.brown-text}

non-linear effects don't have this property

[depending on the type of model]{.pink-text}, having linear effects are nice
:::

## Non-linear example

```{r}
set.seed(1234)
data_toy <- tibble::tibble(
  Predictor = rnorm(100) + 1:100
) |>
  dplyr::mutate(Outcome = sin(Predictor/25) + rnorm(100, sd = 0.1) + 10)
```

```{r}
data_toy |>
  ggplot(aes(Predictor, Outcome)) +
  geom_point() +
  theme_minimal() +
  theme(axis.text = element_blank())
```

## Non-linear example - distance to maximum

```{r}
data_toy |>
  mutate(Color = abs(Predictor - Predictor[max(Outcome) == Outcome])) |>
  ggplot(aes(Predictor, Outcome, color = Color)) +
  geom_point() +
  theme_minimal() +
  theme(axis.text = element_blank()) +
  scale_color_gradient(
    high = "#E0E0E0", 
    low = prismatic::clr_darken("#B5C7EB") |> prismatic::clr_saturate()
  ) +
  guides(color = "none")
  
```

## Non-linear example - splines

```{r}
rec_splines <- recipe(Outcome ~ Predictor, data = data_toy) |>
  step_bs(Predictor, keep_original_cols = TRUE, degree = 7) |>
  prep()

data_splines <- rec_splines |>
  bake(new_data = data_toy) |>
  select(-Predictor_bs_7) |>
  rename_all(\(x) {stringr::str_replace(x, "Predictor_bs_", "Spline Feature ")})

data_splines |>
  tidyr::pivot_longer(cols = -c(Outcome, Predictor)) |>
  ggplot(aes(Predictor, Outcome, color = value)) +
  geom_point() +
  facet_wrap(~name) +
  scale_color_gradient(
    low = "#E0E0E0", 
    high = prismatic::clr_darken("#B5C7EB") |> prismatic::clr_saturate()
  ) +
  theme_minimal() +
  guides(color = "none") +
  theme(axis.text = element_blank())
```

## Basis Spline Features

```{r}
data_splines |>
  select(-Outcome) |>
  tidyr::pivot_longer(cols = -Predictor) |>
  ggplot(aes(Predictor, value)) +
  geom_line() +
  facet_wrap(~name) +
  theme_minimal() +
  theme(axis.text = element_blank())
```

## Monotone Spline Features

```{r}
rec_splines <- recipe(Outcome ~ Predictor, data = data_toy) |>
  step_spline_monotone(Predictor, keep_original_cols = TRUE, degree = 7) |>
  prep()

data_splines <- rec_splines |>
  bake(new_data = data_toy) |>
  select(-c(Predictor_07:Predictor_10)) |>
  rename_all(\(x) {stringr::str_replace(x, "Predictor_0", "Spline Feature ")})

data_splines |>
  select(-Outcome) |>
  tidyr::pivot_longer(cols = -Predictor) |>
  ggplot(aes(Predictor, value)) +
  geom_line() +
  facet_wrap(~name) +
  theme_minimal() +
  theme(axis.text = element_blank())
```

# Categorical Variables {.theme-section4}

##

::: {.speech .pink}
![](assets/cat-theme/profile-01.svg) Dealing with categorical variables are easy right?
:::

::: fragment
::: {.speech .blue .right}
Yes and no, there are some unique strugglesto categoricals ![](assets/cat-theme/profile-02.svg) 
:::
:::

::: fragment
::: {.speech .brown .right}
and there are lots of methods to turn them into numeric ![](assets/cat-theme/profile-04.svg) 
:::
:::

## Character vs Factor variables

![](assets/cat-theme/head-30.svg){.absolute top=50 right=300 width="150" height="150"}
![](assets/cat-theme/head-31.svg){.absolute bottom=50 left=150 width="150" height="150"}

<br>

::: columns
::: {.column width="50%"}
### Character

<br>

[Free form text]{.brown-text}

<br>

no restrictions
:::

::: {.column width="50%"}
### Factor

<br>

[Know possible values]{.purple-text}

<br>

A logical variables is conceptually a factor
:::
:::

## Factor Examples - sex

::: columns
::: {.column width="50%"}
```{r}
adoptions |>
  count(sex) |>
  gt()
```
:::

::: {.column width="50%"}

::: fragment
Lot of information cramped in here

We could have it split into `sex` and `spayed/neutered`
:::

:::
:::

## Factor Examples - intake_condition

::: columns
::: {.column width="50%"}
```{r}
adoptions |>
  count(intake_condition) |>
  slice(1:8) |>
  gt()
```
:::

::: {.column width="50%"}
```{r}
adoptions |>
  count(intake_condition) |>
  slice(9:16) |>
  gt()
```
:::
:::

## Character Examples - promary color

::: columns
::: {.column width="33%"}
```{r}
adoptions |>
  count(primary_color) |>
  slice(1:20) |>
  gt()
```
:::

::: {.column width="33%"}
```{r}
adoptions |>
  count(primary_color) |>
  slice(21:40) |>
  gt()
```
:::

::: {.column width="33%"}
```{r}
adoptions |>
  count(primary_color) |>
  slice(41:60) |>
  gt()
```
:::
:::

## Character Examples - animal name

```{r}
pet_names <- adoptions |>
  drop_na(animal_name) |>
  mutate(animal_name = str_remove(animal_name, "\\*")) |>
  filter(animal_id != animal_name) |>
  filter(str_detect(animal_name, "\\d", negate = TRUE)) |>
  filter(str_detect(animal_name, "^\\s*$", negate = TRUE)) |>
  count(animal_name, sort = TRUE)
```

::: columns
::: {.column width="33%"}
```{r}
pet_names |>
  slice(1:20) |>
  gt()
```
:::

::: {.column width="33%"}
```{r}
pet_names |>
  slice(21:40) |>
  gt()
```
:::

::: {.column width="33%"}
```{r}
pet_names |>
  slice(41:60) |>
  gt()
```
:::
:::

## Character Examples - animal name

```{r}
long_pet_names <- pet_names |>
  filter(n == 1) |>
  mutate(animal_name = str_remove_all(animal_name, "\\*")) |>
  arrange(desc(nchar(animal_name)))
```

::: columns
::: {.column width="50%"}
```{r}
long_pet_names |>
  slice(1:10) |>
  gt()
```
:::

::: {.column width="50%"}
```{r}
long_pet_names |>
  slice(11:20) |>
  gt()
```
:::
:::

## Messy Characters

![](assets/cat-theme/turso-02.svg){.absolute top=50 right=300 width="450" height="450"}


::: {.spacer style="height:70%;"}
Missing values

Inconsistent encoding

Typos

::: fragment
Best dealt with manually
:::
:::

## Unseen Levels

![](assets/cat-theme/turso-03.svg){.absolute top=150 right=100 width="450" height="450"}

<br>

::: {.spacer style="height:50%;"}

Only applicable for [character variables]{.blue-text}

Will depend on [method]{.pink-text} and [models]{.pink-text}

:::

## How to deal with Categorical variables

![](assets/cat-theme/turso-04.svg){.absolute top=150 right=100 width="450" height="450"}

<br>

Non-exhaustive list of methods

<br>

- label / ordinal encoding
- dummy encoding
- frequency encoding
- target encoding

## Label / Ordinal Encoding

![](assets/cat-theme/turso-05.svg){.absolute top=150 right=100 width="450" height="450"}

::: {.spacer style="height:70%;"}

You take the categorical variable

Give each level a number

Replace level with said number

::: fragment
This is unlikely to work well unless done with care
:::
:::

## Label / Ordinal Encoding - Example

```{r}
adoptions |>
  select(sex_before = sex, intake_type_before = intake_type) |>
  mutate(sex_after = sex_before, intake_type_after = intake_type_before) |>
  recipe() |>
  step_integer(sex_after, intake_type_after) |>
  prep() |>
  bake(NULL) |>
  slice(1:12) |>
  gt()
```

## Dummy Encoding

A variable is created for each possible level in categorical variables

They take value 1 when they original variable takes the value, 0 otherwise

::: fragment
::: columns
::: {.column width="50%"}
**pros**

- easy to use and interpret
- Versatile
- base on many other methods
:::

::: {.column width="50%"}
**cons**

- Needs clean levels
- Can create many columns
- Not likely most efficient representation

:::
:::
:::

## Dummy vs One-Hot Encoding

The terms dummy encoding and one-hot encoding get thrown around interchangeably, but they do have different and distinct meanings. 

<br>

One-hot encoding returns k variables

<br>

Dummy Encoding returns k-1 variables

<br>

Dummy encoding is preferred to avoid redundant data

## Dummy Encoding - Example

```{r}
adoptions |>
  select(sex, intake_type) |>
  recipe() |>
  step_dummy(sex, intake_type) |>
  prep() |>
  bake(NULL) |>
  slice(1:12) |>
  gt()
```

## Frequency Encoding

For each level calculate how often it appears

<br>

replace the level with that value

<br>

Can be raw count or percentage (doens't matter much)

## Frequency Encoding - Example

```{r}
adoptions |>
  select(sex_before = sex, intake_type_before = intake_type) |>
  mutate(sex_after = sex_before, intake_type_after = intake_type_before) |>
  recipe() |>
  extrasteps::step_encoding_frequency(sex_after, intake_type_after) |>
  prep() |>
  bake(NULL) |>
  slice(1:12) |>
  gt()
```

## Target Encoding

also called mean encoding, likelihood encoding, or impact encoding

<br>

done by replacing each level of a categorical variable with the [mean of the target variable]{.pink-text} within said level

<br>

The target variable will typically be the outcome, but that is not necessarily a requirement.

## Target Encoding - Example

```{r}
adoptions |>
  select(sex_before = sex, intake_type_before = intake_type, outcome_type) |>
  mutate(sex_after = sex_before, intake_type_after = intake_type_before) |>
  recipe() |>
  embed::step_lencode_glm(sex_after, intake_type_after, outcome = vars(outcome_type)) |>
  prep() |>
  bake(NULL) |>
  slice(1:12) |>
  gt()
```

# Want to learn more? {.theme-section5}

My WIP Book: Feature Engineering A-Z

<https://feaz-book.com/>

Finished books by other people:

- Python Feature Engineering Cookbook
- Feature Engineering Bookcamp
- Feature Engineering and Selection
